Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-25 draft.tex
tiny changes

The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
\begin{align}
\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
\end{align}

@@

%Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
The optimal alternative w.r.t. minimax regret is the one with least max regret. 
Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).
%The computation can be made faster by adopting an efficient scheme of evaluation of PMR where .

>>>>

The maximum regret is considered by assuming that an adversary both 1) can extend the partial profile $\pprofile$ into a complete profile, and 2) can instantiate the weights choosing among any weight vector in $\pw$, where $\pprofile$ and $\pw$ represent our knowledge so far.
We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]
The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
is the worst-case loss of choosing $x$ instead of $y$ under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
\begin{align}
\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
\end{align}

@@

%Finally the minimax regret solution $\MMR(\pprofile, W)$ is determined by solving a sequence of pairwise max regret computations, solving the above linear program for every different pair $(x,y) \in A^{2}$.
The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
The optimal alternative w.r.t. minimax regret is the one with least max regret. 
Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
This idea can be exploited further by adopting a minimax-search tree (see \cite{Braziunas2011}).
%The computation can be made faster by adopting an efficient scheme of evaluation of PMR where .
